### 2019-09-18 2019_neurips_vigil/intro.tex
minor edits

Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.  Potentially, this approach can address Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} and lead to visually grounded language learning.
Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have emerged in the past several years~\cite{mogadala2019trends}. 
Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g. object disappearance).
To deal with the temporal aspect people typically employ cutting the whole video into clips, e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
%As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
%The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
%Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
%For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2015towards}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
However, in real-time dialog or video monitoring, it is impossible to keep the entire history of conversation nor all frames from the beginning of the recording.

>>>>

Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.  Potentially, this approach can address Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} and lead to visually grounded language learning.
Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have emerged in the past several years~\cite{mogadala2019trends}. 
Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g. object disappearance).
To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
%As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
%The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
%Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
%For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2015towards}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.
Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

### 2019-09-18 2019_neurips_vigil/model.tex
Visualization detailed example.
minor edits

\noindent{\textbf{Reasoning Unit.}}
%\paragraph{Reasoning Unit.}
This module is the backbone of SamNet that determines what gating operations need to be performed on the external memory, as well as
determining the location of the correct object for reasoning.
To determine whether we have a valid object from frame (and similarly for memory), we execute the following reasoning procedure.
First, we take the visual attention vector $va_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
and compute a simple aggregate\footnote{%
	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.}: %
$vs_t = \sum_{i=1}^L [va_t(i)]^2$. It can be shown mathematically that the more localized the attention
vector is, the higher is the aggregate value.
We perform a similar computation on the read head $rh_t$ over memory locations.
We feed these 2 values along with the temporal class weights $\tau_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
in $[0,1]$ modulated for the current reasoning step:
(a) $\imatch_t$, which determines whether there is a valid visual object;
(b) $\mmatch_t$, which determines whether there is a valid memory object. 
(c) $\doreplace_t$, which determines whether the memory should be updated by replacing a previously stored object with a new one; and
(d) $\doadd_t$, which determines whether a new object should be added to memory.
We stress that the network has to learn via training how to correctly implement these behaviors.

@@

%For more details of the various modules, please see the appendix.

>>>>

\noindent{\textbf{Reasoning Unit.}}
%\paragraph{Reasoning Unit.}
This module is the backbone of SAMNet that determines what gating operations need to be performed on the external memory, as well as
determining the location of the correct object for reasoning.
To determine whether we have a valid object from the frame (and similarly for memory), we execute the following reasoning procedure.
First, we take the visual attention vector $va_t$ of dimension $L$, where $L$ denotes the number of feature vectors for the frame,
and compute a simple aggregate\footnote{%
	This is closely related to Tsallis entropy of order 2 and to R\'{e}nyi entropy.}: %
$vs_t = \sum_{i=1}^L [va_t(i)]^2$. It can be shown mathematically that the more localized the attention
vector is, the higher is the aggregate value.
We perform a similar computation on the read head $rh_t$ over memory locations.
We feed these two values along with the temporal class weights $\tau_t$ to a 3-layer feedforward classifier with hidden ELU units to extract 4 gating values
in $[0,1]$ modulated for the current reasoning step:
(a) $\imatch_t$, which determines whether there is a valid visual object;
(b) $\mmatch_t$, which determines whether there is a valid memory object. 
(c) $\doreplace_t$, which determines whether the memory should be updated by replacing a previously stored object with a new one; and
(d) $\doadd_t$, which determines whether a new object should be added to memory.
We stress that the network has to learn via training how to correctly implement these behaviors.

@@

For details of the modules not covered here, please see the appendix.
